Light inextensible strings under tension in the Schwarzschild geometry

### 2018-09-06 string.tex
tiny changes

Figure~\ref{closest_approach} shows strings indexed by distance of
approach to the singularity, which occurs at $\phi=0$.  Strings with a
sufficiently close passage to the event horizon self-intersect;
numerical methods show that the critical value is~$\simeq
1.076109317$, with an uncertainty of 1 in the last digit: if a string
with two free ends passes closer than this, it forms a closed loop.

@@

It is possible to parametrize the string in a number of different
ways.  Figure~\ref{angle_at_r_equals_2} shows the same physical
system, but the strings are rotated so that they pass through the
point~$\left(2,0\right)$; the strings are indexed by the
angle~$\alpha$ made with a radius at that point.

>>>>

Figure~\ref{closest_approach} shows strings indexed by distance of
approach to the singularity, which occurs at~$\phi=0$.  Strings with a
sufficiently close passage to the event horizon self-intersect;
numerical methods show that the critical value is~$\simeq
1.076109317$, with an uncertainty of 1 in the last digit: if a string
with two free ends passes closer than this, it forms a closed loop.

@@

It is possible to parametrize the string in a number of different
ways.  Figure~\ref{angle_at_r_equals_2} shows the same physical
system, but the strings are arranged so that they pass through the
point~$\left(2,0\right)$; the strings are indexed by the
angle~$\alpha$ made with a radius at that point.
